Printer ballistics through analysis of character's texture

### 2013-11-17 Printer_Balistics.tex
Editing...

%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
Here goes the introduction and motivation of the work.

Some directions for the paper:

\begin{itemize}
	\item Diagrams and figures are encouraged for making the paper richer
	\item The sections proposed here are not hard-constrained. It means, you 
	can propose other sections as well as change the existing ones. 
\end{itemize}

>>>>

%%% Introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
In August of 2013, a russian man wrote his own small print in a credit card contract. The credit card's administrator bank didn't read the amendments made by the client, and just signed and certified the documents. The alterations included unlimited credit line, 0 percent interest rates and no fees. When the bank decided to terminate man's credit card, because overdue payments, he sued they for more than 24 million rubles (US\$ 727.000). How the bank could prove the falsification?

Legal aspects aside, a way to verify if a document, or a part of it, came from a specific device can be character's texture analysis.
